### 2020-06-26 AlgebraicTopology2020/algtop3/algtop3.tex
Add TOC to everything, along with minor tweaks

	\begin{enumerate}
	\item By definition, we have:
	\begin{equation}
	\begin{tikzcd}[row sep=8.5ex,column sep=5ex]
		& \Delta(\lim F)
			\arrow[d,Rightarrow,"\sigma"] \\
		\Delta(V)
			\arrow[r,Rightarrow,"\eta"]
			\arrow[ur,Rightarrow,dashed,%
				"\exists!\,\Delta(g)"] &
		F
	\end{tikzcd}
	\label{eq:def_limit}
	\end{equation}
	Where $g\colon V\to \lim F$. 
	More intuitively, for the above $F\colon I\to\Cat{Vect}$, this translates to the following diagram in \Cat{Vect}:
	\begin{equation}
	\begin{tikzcd}[row sep=2ex,column sep=8ex]
		&& 0 \\
		V
			\arrow[r,dashed,
				"\exists!\, g"]
			\arrow[urr,bend left,%
				"\eta_\bullet"]
			\arrow[drr,bend right,swap,%
				"\eta_\star"] &
		\lim F
			\arrow[ur,%
				"\sigma_\bullet"]
			\arrow[dr,swap,%
				"\sigma_\star"] & \\
		&& \mbb{R}
	\end{tikzcd}
	\label{eq:lim_in_vect}
	\end{equation}
	\end{enumerate}

@@

	\item

>>>>

	\begin{enumerate}
	\item By definition, we have:
	\begin{equation}
	\begin{tikzcd}[row sep=8.5ex,column sep=5ex]
		& \Delta(\lim F)
			\arrow[d,Rightarrow,"\sigma"] \\
		\Delta(V)
			\arrow[r,Rightarrow,"\eta"]
			\arrow[ur,Rightarrow,dashed,%
				"\exists!\,\Delta(g)"] &
		F
	\end{tikzcd}
	\label{eq:def_limit}
	\end{equation}
	Where $g\colon V\to \lim F$. 
	More intuitively, for the above $F\colon I\to\Cat{Vect}$, this translates to the following diagram in \Cat{Vect}:
	\begin{equation}
	\begin{tikzcd}[row sep=1.5ex,column sep=8ex]
		&& 0 \\
		V
			\arrow[r,dashed,
				"\exists!\, g"]
			\arrow[urr,bend left=25,%
				"\eta_\bullet"]
			\arrow[drr,bend right=25,swap,%
				"\eta_\star"] &
		\lim F
			\arrow[ur,%
				"\sigma_\bullet"]
			\arrow[dr,swap,%
				"\sigma_\star"] & \\
		&& \mbb{R}
	\end{tikzcd}
	\label{eq:lim_in_vect}
	\end{equation}
	\end{enumerate}

@@

	\item \textbf{Composition of pull-backs:}
	\begin{equation}
	\begin{tikzcd}[row sep=7.5ex,column sep=7.5ex]
		Q
			\arrow[ddr,bend right,"g_1",swap]
			\arrow[dr,"f_1"]
			\arrow[drr,"f_2",bend left=12]
			\arrow[drrr,"f_3",bend left=20]
		&[1ex] && \\[-1ex]
		& A_1
			\arrow[rr,"\phi'" description
				,bend left,swap
				,crossing over]
			\arrow[r,dashed]
			\arrow[d] &
		A_2
			\arrow[d]
			\arrow[r,"\phi"] &
		A_3
			\arrow[d] \\
		& B_1
			\arrow[rr,"\psi'" description
				,bend right=25,swap]
			\arrow[r,"\psi",swap,dashed] &
		B_2
			\arrow[from=uull,"g_2",swap
				,bend right=20
				,crossing over]
			\arrow[r] &
		B_3
	\end{tikzcd}
	\end{equation}

	\begin{enumerate}
	\item If $A_1$ is the pull-back of $A_2$ and $A_2$ is the pull-back of $A_3$, then given $Q$ with $f_3,g_1$, we have $g_2 = \psi\circ g_1$, and $f_2$ is fixed uniquely by universal property of $A_2$, while $f_1$ is fixed uniquely by universal property of $A_1$. Hence, $A_1$ is the pull-back of $A_3$.

	\item If $A_1,A_2$ are pull-backs of $A_3$, then given $Q$ with $f_2,g_1$, we have $f_3 = \phi\circ f_2$, and $f_2$ is fixed uniquely by universal property of $A_2$, and $f_1$ is fixed uniquely by universal property of $A_1$. Hence, $A_1$ is the pull-back of $A_3$.
